Combined Task and Motion Planner through an Interface Layer

### 2015-04-18 documentation/draft.tex
edits to tutorial

In order to achieve high level goals a robot must combine task and motion planning. 
A robot uses task planning to determine its long term strategy and motion planning to determine the movements it  will execute to achieve the task. 
Effectively combining task and motion planning is an open research problem. 
We implemented an interface between the motion and task planning. 
Our system uses off-the-shelf task and motion planners and makes few assumptions about their implementation.

@@

Specifically, we start by generating a high level plan and attempting to generate motion plans corresponding to each action.  
When it's not possible to generate a motion plan, the interface layer determines what geometric constraints are causing the problem and relays this back to the task planner in an appropriate format.  
Then, the task planner replans from that set state and the process continues.  
When necessary, backtracking occurs.

@@

\vspace{10}
$PICKUP(obj_1, gripper, pose_1, pose_2, traj)$

@@

\vspace{10}

@@

When the pose generator is called by the interface layer, it generates a set of random poses for each action. Each pose is made up of a set of waypoints. For example for the \textit{pickup} action, it generates the following waypoints: near the cylinder and pointing towards it, touching the cylinder, lifting the cylinder, and a standard home position. It passes one pose to the interface layer at a time, if none of the poses are feasible, the interface layer backtracks resets the pose generator. The TryRefine method of the interface layer attempts to generate a feasible motion plan linking a set of waypoints.

@@

The outer loop of the algorithm interfaces with the high level task planner.  
We start with an initial state where no objects obstruct any motions.  
From there, we look for a high level plan.  
If the problem is not solvable without any problematic environmental information, then the problem is unsolvable and we immediately return that information.  
If we do succeed at finding a high level task plan, we begin the process of attempting to find a motion corresponding to each action.

First, we start by attempting to find a full refinement of the whole plan,calling the TryRefine subroutine in error-free mode.  
If that succeeds, then we return the plan.

@@

>>>>

In order to achieve high level goals a robot must combine task and motion planning. 
A robot uses task planning to determine its long term strategy and motion planning to determine the movements it  will execute to achieve the task. 
Effectively combining task and motion planning is an open research problem. 
We implemented an interface between the motion and task planning based on that outlined in [1]. 
Our system uses off-the-shelf task and motion planners and makes few assumptions about their implementation.

@@

@@

\vspace{10pt}

$PICKUP(obj_1, gripper, pose_1, pose_2, traj)$

@@

\vspace{10pt}

@@

When the pose generator is called by the interface layer, it generates a set of random poses for each action. Each pose is made up of a set of waypoints. For example for the PICKUP action, it generates the following waypoints: near the cylinder and pointing towards it, touching the cylinder, lifting the cylinder, and a standard home position. It passes one pose to the interface layer at a time.  if none of the poses are feasible, the interface layer backtracks and resets the pose generator. The TryRefine method of the interface layer attempts to generate a feasible motion plan between each pose.  The motion planner is called to create this motion plan, including motion plans between waypoints.

@@

The outer loop of the algorithm interfaces with the high level task planner.  
We start with an initial state where no objects obstruct any motions.  
From there, we look for a high level plan.  
If the problem is not solvable even without any obstructions from the environment, then the problem is unsolvable and we immediately return that information.  
If we do succeed at finding a high level task plan, we begin the process of attempting to find a motion corresponding to each action.

First, we start by attempting to find a full refinement of the whole plan, calling the TryRefine subroutine in error-free mode.  
If that succeeds, then we return the plan.

@@

The two immediately relevant open questions are whether it's possible to design a similar interface between task and motion plans which returns optimal plans or which can be used to do online planning.
